Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2024-02-16 Rdocs/Plots.Rmd
saved wq plots as pngs edited wq processing script updated stats script with approrpiate normality and non-parametric tests added NMDS plot

#water quality time series plots by site
#PARAMS:
  #param(string): a string specifying the water quality parameter

wq_ts_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param<- sym(param)
  param_se <- sym(paste(param,"se", sep = "_"))
  ggplot(wq_list$raw_water_quality, aes(x = date, y = !!param, color = site)) +
    #geom layers
    geom_point() +
     geom_smooth(method = 'lm')+
    #labels
    labs(title = paste(param, "Seasonality"), x = "Date")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_color_viridis_d(begin = 0.1, end = 0.9)
}
```

@@

@@

>>>>

#water quality time series plots by site
#PARAMS:
  #param(string): a string specifying the water quality parameter
wq_ts_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param<- sym(param)
  param_se <- sym(paste(param,"se", sep = "_"))
  ggplot(wq_list$summ_water_quality, aes(x = date, y = !!param)) +
    #geom layers
    geom_jitter(height = 0, size = 2) +
     geom_smooth(method = 'lm', se = T)+
    #labels
    labs(title = paste(param, "Seasonality"), x = "Date")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_color_viridis_d()+
  scale_fill_viridis_d()
}

wq_boxplot_BySite <- function(param){
  #create symbol of parameter name and se for tidy eval in ggplot2 call
  param<- sym(param)
  param_se <- sym(paste(param,"se", sep = "_"))
  ggplot(LPP_FullData, aes(x = site, y = !!param, fill = site)) +
    #geom layers
    geom_boxplot()+
    geom_jitter(width = 0.5, height = 0.0, shape = 21, size = 2) +
    #labels
    labs(title = paste(param, "across sites"), x = "Site")+
    #theme adjustments
    theme_bw() +
    theme_rafa(base_size = 15) +
    scale_fill_viridis_d(option = "E",begin = 0.1, end = 0.9)
}
```

@@

wq_boxplot_BySite("P") + labs(y = "Phosphorous (mg/L)", title = "Phosphorous Variation Across Sites")
wq_boxplot_BySite("pH")
wq_boxplot_BySite("NH3")+ labs(y = "Ammonia (mg/L)", title = "Ammonia Variation Across Sites")
wq_boxplot_BySite("Nitrogen")+ labs(y = "Nitrogen (mg/L)", title = "Nitrogen Variation Across Sites")
wq_boxplot_BySite("DO") + labs(y = " % DO")
wq_boxplot_BySite("Flow") + labs(y = "Flow (m/s)", title = "Flow Rate Variation Across Sites")
wq_boxplot_BySite("Cond") + labs(y = "Conductivity (mS)", title = "Conductivity Variation Across Sites")
wq_boxplot_BySite("Temp") + labs(y = "Temp (°C)", title = "Temperature Variation Across Sites")

@@

```{r}
ggplot(wq_list$summ_water_quality) +
  #geom_smooth(aes(x = date,color = site, y = NH3), method = "lm", se = T) +
  geom_point(aes(x = date, fill =site, y = NH3), size = 2.5, shape = 21)+

  scale_fill_viridis_d(option = "D") +
  scale_color_viridis_d(option = "D")

ggplot(wq_list$summ_water_quality, aes(x = NH3, y = site, fill = site)) +
  geom_boxplot() +
  geom_jitter(height = 0.2, width = 0.1, shape = 21, size = 1.5) +
  theme_rafa(base_size = 12)+
  facet_wrap(~date) +
  scale_fill_viridis_d() +
  labs(title = "")
```

```{r}
#plot of first two NMDS dimensions, with ellipses for bag types
ordiplot(taxaCount_NMDS)
ordiellipse(taxaCount_NMDS,LPP_FullData$material, label = FALSE,
            col=viridis(n = 5),
            draw = "polygon", alpha=120) # adding ellipses to the plot, grouping by bag type
title("Similaity of Communities Across Bag Types")
legend("topright", title="Bag type",
       c("Biopolymer", "Cellulose" , "Cotton",  "Jute", "Plastic" ), fill=viridis(n = 5), horiz=FALSE, cex=.9) # adding a legend
```
